Modelling state-switching functional data with hidden Markov models: supplementary material (case study)

### 2021-06-17 Report/Supp_Case.tex
Update Report

        \begin{center}
        \includegraphics[width=2.25in]{../Plots/2019/20190902-182840-CATs_OB_1_0_267_CarHHMM2_coarse-theta-likelihood-dive_duration-1.png}
        \includegraphics[width=2.25in]{../Plots/2019/20190902-182840-CATs_OB_1_0_267_CarHHMM2_coarse-theta-likelihood-dive_duration-2.png}
        \end{center}

@@

        \begin{center}
        \includegraphics[width=2.1in]{../Plots/2019/20190902-182840-CATs_OB_1_0_267_CarHHMM2_coarse-eta-likelihood.png}
        \end{center}

@@

        % Ahat_low
        \begin{center}
        \includegraphics[width=2.1in]{../Plots/2019/20190902-182840-CATs_OB_1_0_267_CarHHMM2_fine-theta-likelihood-Ahat_low-0.png}
        \includegraphics[width=2.1in]{../Plots/2019/20190902-182840-CATs_OB_1_0_267_CarHHMM2_fine-theta-likelihood-Ahat_low-1.png}
        \includegraphics[width=2.1in]{../Plots/2019/20190902-182840-CATs_OB_1_0_267_CarHHMM2_fine-theta-likelihood-Ahat_low-2.png}
        \end{center}

@@

            %\begin{table}[ht]
            %
            %\caption{Estimates and empirical standard errors of emission parameters for dive duration ($Y_t$), acceleration ($\Zone_{t,\tilde t^*}$), and wiggliness ($\Ztwo_{t,\tilde t^*}$) of the killer whale case study data under the full CarHHMM-DFT.}
            \begin{center}
            \scalebox{0.75}{
            \bgroup
            \centering
            \def\arraystretch{1.5}
            \begin{tabular}{ccccc}
            \multirow{2}{*}{Feature}                                                       & \multirow{2}{*}{Dive / Subdive Type} & \multicolumn{3}{c}{Parameter Estimate}        \\
                                                                                           &                                      & $\hat \mu$    & $\hat \sigma$ & $\hat \phi$   \\ \hline
            \multirow{2}{*}{Dive Duration $(s)$ -- $Y_t$}                                  & 1                                    & $27.27 (0.63)$ & $10.91 (0.56)$ & ---           \\
                                                                                           & 2                                    & $127.1 (11.3)$ & $64.1 (9.0)$ & ---           \\ \hline
            \multirow{3}{*}{$x$-Acc. $(m/s^2)$ -- $\left(\Zone_{t,\tilde t^*}\right)_x$}   & 1                                    & $0.423 (0.028)$ & $0.040 (0.001)$ & $0.966 (0.002)$ \\
                                                                                           & 2                                    & $0.210 (0.012)$ & $0.097 (0.002)$ & $0.827 (0.010)$ \\
                                                                                           & 3                                    & $0.232 (0.035)$ & $0.298 (0.010)$ & $0.605 (0.043)$ \\ \hline
            \multirow{3}{*}{$y$-Acc. $(m/s^2)$ -- $\left(\Zone_{t,\tilde t^*}\right)_y$}   & 1                                    & $0.445 (0.036)$ & $0.051 (0.001)$ & $0.966 (0.009)$ \\
                                                                                           & 2                                    & $0.438 (0.012)$ & $0.095 (0.002)$ & $0.827 (0.016)$ \\
                                                                                           & 3                                    & $0.364 (0.043)$ & $0.368 (0.012)$ & $0.605 (0.041)$ \\ \hline
            \multirow{3}{*}{$z$-Acc. $(m/s^2)$ -- $\left(\Zone_{t,\tilde t^*}\right)_z$}   & 1                                    & $-0.680 (0.041)$ & $0.058 (0.001)$ & $0.966 (0.005)$ \\
                                                                                           & 2                                    & $-0.573 (0.014)$ & $0.112 (0.002)$ & $0.827 (0.012)$ \\
                                                                                           & 3                                    & $-0.296 (0.042)$ & $0.357 (0.012)$ & $0.605 (0.039)$ \\ \hline
            \multirow{3}{*}{Wiggliness - $\Ztwo_{t,\tilde t^*}$}                           & 1                                    & $34.98 (0.38)$ & $23.85 (0.39)$ & ---           \\
                                                                                           & 2                                    & $505.8 (5.8)$ & $516.7 (7.0)$ & ---           \\
                                                                                           & 3                                    & $9770 (240)$ & $14460 (380)$ & ---           \\ \hline
            \end{tabular}
            \egroup
            }
            \end{center}

@@

        \subsection{HHMM-DFT}
            \begin{center}
            \scalebox{0.75}{
                \bgroup
                \centering
                \def\arraystretch{1.5}
                \begin{tabular}{ccccc}
                \multirow{2}{*}{Feature}                                                       & \multirow{2}{*}{Dive / Subdive Type} & \multicolumn{3}{c}{Parameter Estimate}          \\
                                                                                               &                                      & $\hat \mu$    & $\hat \sigma$ & $\hat \phi$     \\ \hline
                \multirow{2}{*}{Dive Duration $(s)$ -- $Y_t$}                                  & 1                                    & $26.565 (0.607)$ & $10.118 (0.518)$ & ---             \\
                                                                                               & 2                                    & $116.134 (10.584)$ & $64.778 (8.543)$ & ---             \\ \hline
                \multirow{3}{*}{$x$-Acc. $(m/s^2)$ -- $\left(\Zone_{t,\tilde t^*}\right)_x$}   & 1                                    & $-0.001 (0.002)$ & $0.064 (0.001)$ & ---             \\
                                                                                               & 2                                    & $0.084 (0.004)$ & $0.173 (0.003)$ & ---             \\
                                                                                               & 3                                    & $0.287 (0.020)$ & $0.481 (0.014)$ & ---             \\ \hline
                \multirow{3}{*}{$y$-Acc. $(m/s^2)$ -- $\left(\Zone_{t,\tilde t^*}\right)_y$}   & 1                                    & $0.365 (0.002)$ & $0.067 (0.001)$ & ---             \\
                                                                                               & 2                                    & $0.408 (0.002)$ & $0.107 (0.002)$ & ---             \\
                                                                                               & 3                                    & $0.278 (0.016)$ & $0.403 (0.012)$ & ---             \\ \hline
                \multirow{3}{*}{$z$-Acc. $(m/s^2)$ -- $\left(\Zone_{t,\tilde t^*}\right)_z$}   & 1                                    & $-0.441 (0.003)$ & $0.101 (0.002)$ & ---             \\
                                                                                               & 2                                    & $-0.471 (0.003)$ & $0.157 (0.002)$ & ---             \\
                                                                                               & 3                                    & $-0.300 (0.017)$ & $0.412 (0.012)$ & ---             \\ \hline
                \multirow{3}{*}{Wiggliness - $\Ztwo_{t,\tilde t^*}$}                           & 1                                    & $42.149 (0.507)$ & $32.091 (0.554)$ & ---             \\
                                                                                               & 2                                    & $584.178 (6.491)$ & $687.082 (8.805)$ & ---             \\
                                                                                               & 3                                    & $6841.607 (148.113)$ & $13060.895 (293.086)$ & ---             \\ \hline
                \end{tabular}
                \egroup
            }
            \end{center}

@@

            \begin{center}
            \scalebox{0.75}{
                \bgroup
                \centering
                \def\arraystretch{1.5}
                \begin{tabular}{ccccc}
                \multirow{2}{*}{Feature}                                                       & \multirow{2}{*}{Dive / Subdive Type} & \multicolumn{3}{c}{Parameter Estimate}        \\
                                                                                               &                                      & $\hat \mu$    & $\hat \sigma$ & $\hat \phi$   \\ \hline
                \multirow{2}{*}{Dive Duration $(s)$ -- $Y_t$}                                  & 1                                    & $27.170 (0.629)$ & $10.821 (0.552)$ & ---           \\
                                                                                               & 2                                    & $125.090 (11.003)$ & $64.488 (8.842)$ & ---           \\ \hline
                \multirow{3}{*}{$x$-Acc. $(m/s^2)$ -- $\left(\Zone_{t,\tilde t^*}\right)_x$}   & 1                                    & $0.066 (0.017)$ & $0.035 (0.002)$ & $0.876 (0.006)$ \\
                                                                                               & 2                                    & $0.339 (0.037)$ & $0.095 (0.011)$ & $0.878 (0.037)$ \\
                                                                                               & 3                                    & $0.258 (0.007)$ & $0.305 (0.001)$ & $0.605 (0.010)$ \\ \hline
                \multirow{3}{*}{$y$-Acc. $(m/s^2)$ -- $\left(\Zone_{t,\tilde t^*}\right)_y$}   & 1                                    & $0.377 (0.017)$ & $0.044 (0.002)$ & $0.876 (0.014)$ \\
                                                                                               & 2                                    & $0.469 (0.045)$ & $0.097 (0.013)$ & $0.878 (0.042)$ \\
                                                                                               & 3                                    & $0.349 (0.009)$ & $0.378 (0.001)$ & $0.605 (0.013)$ \\ \hline
                \multirow{3}{*}{$z$-Acc. $(m/s^2)$ -- $\left(\Zone_{t,\tilde t^*}\right)_z$}   & 1                                    & $-0.464 (0.020)$ & $0.052 (0.002)$ & $0.876 (0.010)$ \\
                                                                                               & 2                                    & $-0.658 (0.045)$ & $0.113 (0.013)$ & $0.878 (0.040)$ \\
                                                                                               & 3                                    & $-0.305 (0.011)$ & $0.370 (0.001)$ & $0.605 (0.012)$ \\ \hline
                \end{tabular}
                \egroup
            }
            \end{center}

@@

            \begin{center}
            \scalebox{0.75}{
                \bgroup
                \centering
                \def\arraystretch{1.5}
                \begin{tabular}{ccccc}
                \multirow{2}{*}{Feature}                                                       & \multirow{2}{*}{Dive / Subdive Type} & \multicolumn{3}{c}{Parameter Estimate}        \\
                                                                                               &                                      & $\hat \mu$    & $\hat \sigma$ & $\hat \phi$   \\ \hline
                \multirow{1}{*}{Dive Duration $(s)$ -- $Y_t$}                                  & 1                                    & $41.875 (1.249)$ & $30.633 (1.230)$ & ---           \\ \hline
                \multirow{3}{*}{$x$-Acc. $(m/s^2)$ -- $\left(\Zone_{t,\tilde t^*}\right)_x$}   & 1                                    & $0.455 (0.030)$ & $0.039 (0.001)$ & $0.968 (0.002)$ \\
                                                                                               & 2                                    & $0.214 (0.012)$ & $0.096 (0.002)$ & $0.832 (0.009)$ \\
                                                                                               & 3                                    & $0.222 (0.034)$ & $0.295 (0.010)$ & $0.604 (0.039)$ \\ \hline
                \multirow{3}{*}{$y$-Acc. $(m/s^2)$ -- $\left(\Zone_{t,\tilde t^*}\right)_y$}   & 1                                    & $0.456 (0.039)$ & $0.051 (0.001)$ & $0.968 (0.009)$ \\
                                                                                               & 2                                    & $0.437 (0.012)$ & $0.094 (0.002)$ & $0.832 (0.016)$ \\
                                                                                               & 3                                    & $0.366 (0.042)$ & $0.364 (0.012)$ & $0.604 (0.040)$ \\ \hline
                \multirow{3}{*}{$z$-Acc. $(m/s^2)$ -- $\left(\Zone_{t,\tilde t^*}\right)_z$}   & 1                                    & $-0.700 (0.044)$ & $0.058 (0.001)$ & $0.968 (0.005)$ \\
                                                                                               & 2                                    & $-0.574 (0.014)$ & $0.111 (0.002)$ & $0.832 (0.012)$ \\
                                                                                               & 3                                    & $-0.302 (0.041)$ & $0.354 (0.012)$ & $0.604 (0.039)$ \\ \hline
                \multirow{3}{*}{Wiggliness - $\Ztwo_{t,\tilde t^*}$}                           & 1                                    & $33.883 (0.367)$ & $22.847 (0.376)$ & ---           \\
                                                                                               & 2                                    & $480.622 (5.479)$ & $492.201 (6.598)$ & ---           \\
                                                                                               & 3                                    & $9987.824 (239.804)$ & $14754.912 (375.450)$ & ---           \\ \hline
                \end{tabular}
                \egroup
            }
            \end{center}

>>>>

        \begin{center}
        %\includegraphics[width=2.25in]{../Plots/2019/20190902-182840-CATs_OB_1_0_267_CarHHMM2_coarse-theta-likelihood-dive_duration-1.png}
        %\includegraphics[width=2.25in]{../Plots/2019/20190902-182840-CATs_OB_1_0_267_CarHHMM2_coarse-theta-likelihood-dive_duration-2.png}
        \end{center}

@@

        \begin{center}
        %\includegraphics[width=2.1in]{../Plots/2019/20190902-182840-CATs_OB_1_0_267_CarHHMM2_coarse-eta-likelihood.png}
        \end{center}

@@

        % Ahat_low
        \begin{center}
        %\includegraphics[width=2.1in]{../Plots/2019/20190902-182840-CATs_OB_1_0_267_CarHHMM2_fine-theta-likelihood-Ahat_low-0.png}
        %\includegraphics[width=2.1in]{../Plots/2019/20190902-182840-CATs_OB_1_0_267_CarHHMM2_fine-theta-likelihood-Ahat_low-1.png}
        \includegraphics[width=2.1in]{../Plots/2019/20190902-182840-CATs_OB_1_0_267_CarHHMM2_fine-theta-likelihood-Ahat_low-2.png}
        \end{center}

@@

            %\begin{table}[ht]
            %
            %\caption{Estimates and empirical standard errors of emission parameters for dive duration ($Y_t$), acceleration ($\Zone_{t,\tilde t^*}$), and wiggliness ($\Ztwo_{t,\tilde t^*}$) of the killer whale case study data under the full CarHHMM-DFT.}
            \begin{center}
            \scalebox{0.75}{
            \bgroup
            \centering
            \def\arraystretch{1.5}
            \begin{tabular}{ccccc}
                \multirow{2}{*}{Feature}                                                       & \multirow{2}{*}{Dive / Subdive Type} & \multicolumn{3}{c}{Parameter Estimate}        \\
                                                                                               &                                      & $\hat \mu$    & $\hat \sigma$ & $\hat \phi$   \\ \hline
                \multirow{2}{*}{Dive Duration $(s)$ -- $Y_t$}                                  & 1                                    & $27.34 (0.63)$ & $10.96 (0.56)$ & ---           \\
                                                                                               & 2                                    & $127.5 (11.3)$ & $63.9 (9.0)$ & ---           \\ \hline
                \multirow{3}{*}{$x$-Acc. $(m/s^2)$ -- $\left(\Zone_{t,\tilde t^*}\right)_x$}   & 1                                    & $0.449 (0.030)$ & $0.039 (0.001)$ & $0.968 (0.002)$ \\
                                                                                               & 2                                    & $0.210 (0.012)$ & $0.096 (0.002)$ & $0.829 (0.010)$ \\
                                                                                               & 3                                    & $0.232 (0.035)$ & $0.296 (0.010)$ & $0.607 (0.042)$ \\ \hline
                \multirow{3}{*}{$y$-Acc. $(m/s^2)$ -- $\left(\Zone_{t,\tilde t^*}\right)_y$}   & 1                                    & $0.450 (0.038)$ & $0.051 (0.001)$ & $0.968 (0.009)$ \\
                                                                                               & 2                                    & $0.437 (0.012)$ & $0.094 (0.002)$ & $0.829 (0.016)$ \\
                                                                                               & 3                                    & $0.366 (0.042)$ & $0.365 (0.012)$ & $0.607 (0.040)$ \\ \hline
                \multirow{3}{*}{$z$-Acc. $(m/s^2)$ -- $\left(\Zone_{t,\tilde t^*}\right)_z$}   & 1                                    & $-0.691 (0.043)$ & $0.058 (0.001)$ & $0.968 (0.005)$ \\
                                                                                               & 2                                    & $-0.573 (0.014)$ & $0.111 (0.002)$ & $0.829 (0.012)$ \\
                                                                                               & 3                                    & $-0.303 (0.041)$ & $0.354 (0.012)$ & $0.607 (0.039)$ \\ \hline
                \multirow{3}{*}{Wiggliness - $\Ztwo_{t,\tilde t^*}$}                           & 1                                    & $34.02 (0.36)$ & $22.99 (0.38)$ & ---           \\
                                                                                               & 2                                    & $490.1 (5.6)$ & $502.6 (6.8)$ & ---           \\
                                                                                               & 3                                    & $9150 (220)$ & $13540 (350)$ & ---           \\ \hline
            \end{tabular}
            \egroup
            }
            \end{center}

@@

        \subsection{HHMM-DFT}
            \begin{center}
            \scalebox{0.75}{
                \bgroup
                \centering
                \def\arraystretch{1.5}
                \begin{tabular}{ccccc}
                \multirow{2}{*}{Feature}                                                       & \multirow{2}{*}{Dive / Subdive Type} & \multicolumn{3}{c}{Parameter Estimate}          \\
                                                                                               &                                      & $\hat \mu$    & $\hat \sigma$ & $\hat \phi$     \\ \hline
                \multirow{2}{*}{Dive Duration $(s)$ -- $Y_t$}                                  & 1                                    & $26.61 (0.61)$ & $10.16 (0.52)$ & ---             \\
                                                                                               & 2                                    & $116.8 (10.6)$ & $64.7 (8.6)$ & ---             \\ \hline
                \multirow{3}{*}{$x$-Acc. $(m/s^2)$ -- $\left(\Zone_{t,\tilde t^*}\right)_x$}   & 1                                    & $0.000 (0.002)$ & $0.065 (0.001)$ & ---             \\
                                                                                               & 2                                    & $0.085 (0.004)$ & $0.175 (0.003)$ & ---             \\
                                                                                               & 3                                    & $0.291 (0.020)$ & $0.484 (0.014)$ & ---             \\ \hline
                \multirow{3}{*}{$y$-Acc. $(m/s^2)$ -- $\left(\Zone_{t,\tilde t^*}\right)_y$}   & 1                                    & $0.365 (0.002)$ & $0.068 (0.001)$ & ---             \\
                                                                                               & 2                                    & $0.408 (0.002)$ & $0.108 (0.002)$ & ---             \\
                                                                                               & 3                                    & $0.275 (0.017)$ & $0.407 (0.012)$ & ---             \\ \hline
                \multirow{3}{*}{$z$-Acc. $(m/s^2)$ -- $\left(\Zone_{t,\tilde t^*}\right)_z$}   & 1                                    & $-0.442 (0.003)$ & $0.101 (0.002)$ & ---             \\
                                                                                               & 2                                    & $-0.471 (0.003)$ & $0.158 (0.002)$ & ---             \\
                                                                                               & 3                                    & $-0.298 (0.017)$ & $0.415 (0.012)$ & ---             \\ \hline
                \multirow{3}{*}{Wiggliness - $\Ztwo_{t,\tilde t^*}$}                           & 1                                    & $43.65 (0.52)$ & $33.66 (0.58)$ & ---             \\
                                                                                               & 2                                    & $608.0 (6.8)$ & $717.3 (9.2)$ & ---             \\
                                                                                               & 3                                    & $7100 (160)$ & $13620 (310)$ & ---             \\ \hline
                \end{tabular}
                \egroup
            }
            \end{center}

@@

            \begin{center}
            \scalebox{0.75}{
                \bgroup
                \centering
                \def\arraystretch{1.5}
                \begin{tabular}{ccccc}
                \multirow{2}{*}{Feature}                                                       & \multirow{2}{*}{Dive / Subdive Type} & \multicolumn{3}{c}{Parameter Estimate}        \\
                                                                                               &                                      & $\hat \mu$    & $\hat \sigma$ & $\hat \phi$   \\ \hline
                \multirow{2}{*}{Dive Duration $(s)$ -- $Y_t$}                                  & 1                                    & $27.16 (0.63)$ & $10.78 (0.55)$ & ---           \\
                                                                                               & 2                                    & $124.2 (11.0)$ & $64.6 (8.8)$ & ---           \\ \hline
                \multirow{3}{*}{$x$-Acc. $(m/s^2)$ -- $\left(\Zone_{t,\tilde t^*}\right)_x$}   & 1                                    & $0.064 (0.007)$ & $0.035 (0.001)$ & $0.874 (0.008)$ \\
                                                                                               & 2                                    & $0.342 (0.017)$ & $0.095 (0.002)$ & $0.879 (0.005)$ \\
                                                                                               & 3                                    & $0.257 (0.037)$ & $0.305 (0.010)$ & $0.605 (0.023)$ \\ \hline
                \multirow{3}{*}{$y$-Acc. $(m/s^2)$ -- $\left(\Zone_{t,\tilde t^*}\right)_y$}   & 1                                    & $0.376 (0.009)$ & $0.044 (0.001)$ & $0.874 (0.008)$ \\
                                                                                               & 2                                    & $0.470 (0.017)$ & $0.097 (0.002)$ & $0.879 (0.005)$ \\
                                                                                               & 3                                    & $0.350 (0.045)$ & $0.377 (0.013)$ & $0.605 (0.023)$ \\ \hline
                \multirow{3}{*}{$z$-Acc. $(m/s^2)$ -- $\left(\Zone_{t,\tilde t^*}\right)_z$}   & 1                                    & $-0.462 (0.011)$ & $0.052 (0.001)$ & $0.874 (0.008)$ \\
                                                                                               & 2                                    & $-0.660 (0.020)$ & $0.113 (0.002)$ & $0.879 (0.005)$ \\
                                                                                               & 3                                    & $-0.306 (0.045)$ & $0.369 (0.013)$ & $0.605 (0.023)$ \\ \hline
                \end{tabular}
                \egroup
            }
            \end{center}

@@

        \subsection{CarHMM-DFT}
            \begin{center}
            \scalebox{0.75}{
                \bgroup
                \centering
                \def\arraystretch{1.5}
            \begin{tabular}{ccccc}
            \multirow{2}{*}{Feature}                                                       & \multirow{2}{*}{Dive / Subdive Type} & \multicolumn{3}{c}{Parameter Estimate}        \\
                                                                                           &                                      & $\hat \mu$    & $\hat \sigma$ & $\hat \phi$   \\ \hline
            \multirow{1}{*}{Dive Duration $(s)$ -- $Y_t$}                                  & 1                                    & $41.70 (1.24)$ & $30.50 (1.22)$ & ---           \\ \hline
            \multirow{3}{*}{$x$-Acc. $(m/s^2)$ -- $\left(\Zone_{t,\tilde t^*}\right)_x$}   & 1                                    & $0.460 (0.030)$ & $0.039 (0.001)$ & $0.968 (0.002)$ \\
                                                                                           & 2                                    & $0.209 (0.012)$ & $0.096 (0.002)$ & $0.828 (0.007)$ \\
                                                                                           & 3                                    & $0.232 (0.035)$ & $0.296 (0.010)$ & $0.607 (0.023)$ \\ \hline
            \multirow{3}{*}{$y$-Acc. $(m/s^2)$ -- $\left(\Zone_{t,\tilde t^*}\right)_y$}   & 1                                    & $0.457 (0.038)$ & $0.052 (0.001)$ & $0.968 (0.002)$ \\
                                                                                           & 2                                    & $0.436 (0.012)$ & $0.094 (0.002)$ & $0.828 (0.007)$ \\
                                                                                           & 3                                    & $0.365 (0.042)$ & $0.366 (0.012)$ & $0.607 (0.023)$ \\ \hline
            \multirow{3}{*}{$z$-Acc. $(m/s^2)$ -- $\left(\Zone_{t,\tilde t^*}\right)_z$}   & 1                                    & $-0.704 (0.044)$ & $0.059 (0.001)$ & $0.968 (0.002)$ \\
                                                                                           & 2                                    & $-0.571 (0.014)$ & $0.111 (0.002)$ & $0.828 (0.007)$ \\
                                                                                           & 3                                    & $-0.301 (0.042)$ & $0.355 (0.012)$ & $0.607 (0.023)$ \\ \hline
            \multirow{3}{*}{Wiggliness - $\Ztwo_{t,\tilde t^*}$}                           & 1                                    & $34.40 (0.37)$ & $23.33 (0.38)$ & ---           \\
                                                                                           & 2                                    & $495.0 (5.7)$ & $505.4 (6.9)$ & ---           \\
                                                                                           & 3                                    & $9190 (220)$ & $13590 (360)$ & ---           \\ \hline
            \end{tabular}
                \egroup
            }
            \end{center}
